---
title: "Evapotranspiration Data"
author: "Alysa M. Yoder"
date: "June 20, 2018"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
    theme: flatly
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE,
                      error = FALSE, 
                      cache = TRUE, 
                      eval = TRUE)
library(here)
```

# Download and plot actual ET data from Toby, CA BCM 30 yr avg 
* This data looks different than what I'm seeing on the BCM website. Re-downloading the same data doesn't work, doesn't give a functional .tif file. 
```{r}
library(here)
library(raster)
library(sp)
et <- raster("C:/Users/ayoder/Box Sync/Cosumnes/ET/aet1981_2010_ave_HST_1463959465/aet1981_2010_ave_HST_1463959465.tif")
spplot(et, col.regions = rev(get_col_regions()), main = "GCM ET Data")
```

# Extract data for Oneto-Denier
```{r}
#raster  extraction
library(raster)
aet<-raster("C:/Users/ayoder/Box Sync/Cosumnes/ET/aet1981_2010_ave_HST_1463959465/aet1981_2010_ave_HST_1463959465.tif")
library(sp)
library(rgdal)
#shape<-readOGR(dsn="C:/Users/ayoder/Documents/R/OD_recharge/data", layer = "OD_poly")
shape <- shapefile(here::here("data", "OD_poly.shp"))
shape<-spTransform(shape, crs(aet))

#extract data masked with chosen shapefile
temp <- raster::mask(aet, shape) #extract only the ET values that are within the shape. Gives NA values which are removed in the next chunk. 

#plot the masked AET raster
plot(temp, xlim = bbox(shape)[1,], ylim = bbox(shape)[2,], main = "30 yr Mean AET for 1 WY at OD")
plot(shape, add=T)
```

# Calculate volume/rate of ET from Toby data
```{r}
library(dplyr)
et_vals <- as.data.frame(temp@data@values) #df with just the values of ET in the OD floodplain
mean_et <- sapply(et_vals, mean, na.rm=TRUE) # mean ET value in mm/71556.81m^2*day

#convert to a volume of ET throughout the water year 
#using the same method that I use to get a volume from my interpolated change in head rasters
#refer to rech_fxn.R

#make sure to convert temp to m before multiplying by the area of each cell 
m3_aet <- prod(res(temp)) * (temp/1000)
volaet <- cellStats(m3_aet, "sum") #total volume of ET over 1 WY in cubic meters

tempinfo <- as.data.frame(freq(temp, useNA="no"))
ncelltemp <- sum(tempinfo$count)
mET <- volaet/(ncelltemp*(prod(res(temp)))) #matches the mean_et value calculated above 
```

# Analyze this ET number with yearly recharge estimates
* this estimate of aet is very significant when considered with rech estimates
* this could be because the recharge estimate time spans don't occur throughout the entire water year. Times when recharge occurs(Dec-May) do align with (Mar-May) historical times of higher AET. 
```{r}
library(knitr)
rcdf <- read.csv(here::here("data", "clipped_2014_17_rechargeVols.csv"), 
                 header = TRUE, 
                 stringsAsFactors = FALSE, 
                nrows = 4)[ ,1:4] #bracket subset is a workaround for the absence of a 'ncols' option like 'nrows'
rcdf$AETVol_divby_MidRechVol <- volaet/(rcdf$MidRecharge) 
kable(rcdf)
```

***
# Newly downloaded historical ET data, crosscheck w/data from Toby
* something is wrong with this .tif, data will plot, but doesn't match what shows up on the BCM online map interface. et2@data@values shows up having no data, max and min is inf and -inf. 
```{r}
library(here)
library(raster)
library(sp)
library(dplyr)
et2 <- raster(here::here("rasters", "aet1971_2000ave_HST_1530123260", "aet1971_2000ave_HST_1530123260.tif"))

plot(et2)
plot(shape, add=T)

et2_up <- as.data.frame(et2@data@values) %>% na.omit()
mean_et2 <- sapply(et2_up, mean, na.rm=TRUE)
mean_et2
```

