---
title: "GO Well Locations"
author: "Alysa M. Yoder"
date: "October 12, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## UC Water Groundwater Observatory Well Locations
Zoom in and mouse over to see well labels. 
The purple markers show locations in the area we need to monitor. We are looking for wells to monitor in the vicinity of these purple markers, they do not have to be exactly in the marked locations.
All wells except the purple are existing wells that could be a part of the observatory. 
```{r, echo = FALSE, message = FALSE}
library(leaflet)
well <- read.csv('OHWD.csv')
od <- read.csv('ohwd_od.csv')
cor <- read.csv('ohwd_cor.csv')
rech <- read.csv('ohwd_rech.csv')
fake <- read.csv('GO_desirable_fake_wells.csv')

m <- leaflet() %>% fitBounds(lng1 = -121.39, lat1 = 38.227236, lng2 = -121.022671, lat2 = 38.5599) %>%
      addTiles() %>%
      addCircleMarkers(data = od, popup = ~as.character(name), label = ~as.character(name), labelOptions = labelOptions(noHide = TRUE, textsize='8pt', textOnly = T),
                       color = 'red', 
                       radius = 2, weight = 5,              
                       opacity = 1) %>% #Oneto-Denier
      addCircleMarkers(data = cor, popup = ~as.character(name), label = ~as.character(name), labelOptions = labelOptions(noHide = TRUE, textsize='8pt', textOnly = T), 
                       color = 'black', 
                       radius = 2, 
                       weight = 5, 
                       opacity = 1) %>% #Cosumnes Corridor
      addCircleMarkers(data = rech, popup = ~as.character(name), label = ~as.character(name), labelOptions = labelOptions(noHide = TRUE, textsize='8pt', textOnly = T),
                       color = 'blue', 
                       radius = 2, 
                       weight = 5, 
                       opacity = 1) %>% #Recharge Project
#      addCircleMarkers(data = fake, label = ~as.character(name), labelOptions = labelOptions(noHide = TRUE, textsize='5pt', textOnly = T),
#                       color = 'purple', 
  #                     radius = 2, 
   #                    weight = 5, 
    #                   opacity = 1) %>% #Fake Potential Well Locations
      addProviderTiles(providers$Esri.WorldImagery) %>%
      addScaleBar(position = c("topright")) %>%
      addLegend(position = c("bottomright"), colors = c('red', 'blue', 'black', 'purple'), labels = c('Oneto-Denier', 
                                                                                            'Recharge Project',
                                                                                            'Available GO Wells',
                                                                                            'Desirable Monitoring Locations'),
                title = 'Well Category')

m
```

