---
title: "Oneto-Denier Recharge Estimates for the 2016-17 Water Year"
output: 
  html_document:
    code_folding: hide
    toc: TRUE
    toc_float: TRUE
author: Amy Yoder
---

```{r global_options, include=FALSE}
library(knitr)
opts_chunk$set(warning=FALSE, message=FALSE)
```

```{r, message = FALSE, warning = FALSE, results = "hide", echo=FALSE}
# setwd()
setwd("~/GitHub/OD_recharge")

# load packages
packagelist = list("ggplot2", "colorspace", "reshape2", "tidyverse", "knitr", "sp", 
                   "rgdal", "raster", "gstat", "dismo", "spMC", "formatR", "dplyr", "magrittr")
lapply(packagelist, library, character.only = TRUE)

# read in data frames, convert to SPDF
low <- read.csv("R_input_low_1617.csv")
high <- read.csv('R_input_high_1617.csv')
coordinates(high) <- ~ long + lat
coordinates(low) <- ~ long + lat
```

## Min & Max Surface Water Levels
Shows locations of monitoring wells at the Oneto-Denier field site. Marker size increases with magnitude of surface water level (meters). 
```{r, tidy=TRUE}
# plot surface water levels

low %>% as.data.frame %>% 
  ggplot(aes(long, lat)) + geom_point(aes(size=levellow), color="blue", alpha=3/4) + 
  ggtitle("Lowest Surface Water Level (m)") + coord_equal() + theme_bw()

high %>% as.data.frame %>% 
  ggplot(aes(long, lat)) + geom_point(aes(size=levelhigh), color="blue", alpha=3/4) + 
  ggtitle("Highest Surface Water Level (m)") + coord_equal() + theme_bw()

```

## Kriged Recharge Estimates
Using ordinary kriging.
```{r}
suppressPackageStartupMessages({
  library(gstat)
})
x <- seq(from=min(high$lat), to=max(high$lat), by=(max(high$lat)-min(high$lat))/6)
y <- seq(from=min(high$long), to=max(high$long), by=(max(high$long)-min(high$long))/6)
# krige low----

# variograms
#low
lzn.vgm <- variogram(log(low$levellow*-1)~1, low) # calculate sample variogram values
lzn.fit <- fit.variogram(lzn.vgm, model=vgm(psill = 10, "Sph", range = NA, kappa = 0.5)) # fit model
plot(lzn.vgm, lzn.fit, main='Variogram for Low Water Levels')
#high
h.vgm <- variogram(log(high$levelhigh)~1, data = high) 
h.fit <- fit.variogram(h.vgm, model=vgm(psill = .1, "Lin", range = NA))
plot(h.vgm, h.fit, main='Variogram for High Water Levels')

# load spatial domain to interpolate over
grid <- raster(low, ncols=100, nrows=100)
g<-as(grid, 'SpatialGrid')

# krige low
k <- gstat(formula = low$levellow~1, locations = low, model = lzn.fit)
kriged <- predict(k,g)
plot(kriged, main='Lowest SWL(m) of the 2016-17 Water Year, Kriged', axes=TRUE)
plot(low, add = T)

# krige high
kh <- gstat(formula = high$levelhigh~1, locations = high, model = h.fit)
krigedh <- predict(kh, g)
plot(krigedh, main='Highest SWL(m) of the 2016-17 Water Year, Kriged', axes=TRUE)
plot(high, add = T)

# krige difference----
rash <- raster(krigedh)
rasl <- raster(kriged)
krige1617 <- rash-rasl
par(mfrow=c(1,1))
plot(krige1617, col = rainbow(100), main = expression("2016-17 Wet-Season Cumulative "*Delta*" Head(m) w/Kriging"), 
     alpha = .5, axes=TRUE)
plot(high, add = T)

# krige recharge estimate----
ac_per_cell <- 1136/10000
krige1617feet <- krige1617*3.28084
sum_krige_ft <- cellStats(krige1617feet, 'sum')
krig_rech1617_acft <- sum_krige_ft*ac_per_cell

```

## IDW Recharge Estimates
Recharge estimates calculated with inverse distance weighting
```{r}
library(gstat)
library(dplyr)
library(ggplot2)
# idw high----

hi <- gstat(formula = high$levelhigh~1, locations = high, nmax=8, set=list(idp=2))
idw_h <- interpolate(grid, hi)
plot(idw_h, main = 'Highest SWL(m)')
plot(high, add=T)

# idw low ----
gs<-gstat(formula = low$levellow~1, locations = low, nmax=8, set=list(idp=2))
idw<-interpolate(grid, gs)
plot(idw, main = 'Lowest SWL (m)')
plot(low, add=T)
# inverse distance weighting difference----
idw1617 <- idw_h - idw

plot(idw1617, main = expression("2016-17 Wet-Season Cumulative "*Delta*" Head(m)"), col = rainbow(100), alpha = 0.5)
plot(high, add=T)

# idw recharge estimate----
idw1617feet <- idw1617*3.28084
ac_per_cell <- 1136/10000
sum_idw_ft <- cellStats(idw1617feet, 'sum')
rech1617_acft <- sum_idw_ft*ac_per_cell

# 1/30/17 - 2/16/17 Flood Event Recharge
l_ev <- as.data.frame(read.csv('event1_low.csv'))
h_ev <- as.data.frame(read.csv('event1_high.csv'))
# convert to SPDFs
coordinates(h_ev) <- ~ long + lat
coordinates(l_ev) <- ~ long + lat


# load spatial domain to interpolate over
grid2 <- raster(l_ev, ncols=100, nrows=100)
# interpolate highs
hi2 <- gstat(formula = h_ev$hlevel~1, locations = h_ev, nmax = 8, set=list(idp=2))
ev_idw_h <- interpolate(grid2, hi2)
# interpolate lows
lo2 <- gstat(formula = l_ev$llevel~1, locations = l_ev, nmax = 8, set = list(idp=2))
ev_idw_l <- interpolate(grid2, lo2)
# high idw - low idw
idw_event <- ev_idw_h - ev_idw_l
plot(idw_event)
# calculate event recharge volume 1/30/17-2/16/17
idw_event_ft <- idw_event*3.28084
ac_per_cell <- 1136/10000
sum_idw_event_ft <- cellStats(idw_event_ft, 'sum')
rech_event_acft <- sum_idw_event_ft*ac_per_cell
# multiply rech_event_acft by specific yield, calculate acft/ac


# import outline of boundary, as a set of points in lat/long that we generated in ArcMap as a digitized polyline
bound <- read.csv("bound_table.csv", stringsAsFactors = FALSE, header = TRUE)
bound_pts <- bound[,c(4,5)]
colnames(bound_pts) <- c('x', 'y')

# convert raster to SPDF, or at least get some coords
idwevent_pts <- coordinates(idw_event)[!is.na(values(idw_event)),]
colnames(idwevent_pts) <- c('x', 'y')

# clip event idw by the innundation extent generated form our digitized polyline in ArcMap
library(splancs)
temp <- rasterToPoints(idw_event) %>% as.data.frame()
idwevent_clip <- temp[inout(idwevent_pts, bound_pts), ]
colnames(idwevent_clip) <- c('x','y','z')

# plot idwevent_clip as a heatmap
library(viridis)
library(magrittr)
idwevent_clip %>% 
  ggplot() +
  geom_tile(aes(x,y, fill = z)) +
  coord_fixed(1) +
  scale_fill_viridis(name="Event Recharged Head (m)") +
  theme_void()

coordinates(idwevent_clip) <- ~ x + y
gridded(idwevent_clip) <- TRUE
idwevent_rast <- raster(idwevent_clip, "z")
plot(idwevent_rast)
# export tif to use for plotting
writeRaster(idwevent_rast, "/Users/ayoder/Desktop/finalevent3.GTiff", format = "GTiff")

amyraster<-raster("/Users/ayoder/Desktop/finalevent.tif", ncols=1000,nrows=1000)
```

## Map of the Oneto-Denier Field Site
Generated with ggmap. 
```{r}
suppressPackageStartupMessages({
  library(ggmap)
})
b <- bbox(low)
(OD_map <- ggmap(get_map(location = b))) #download map for Oneto-Denier 
```

## 2016-17 Recharge Estimate Ineractive Plots
Kriged and inverse distance weighted recharge estimates overlaid on basemaps. Mouse over markers to see monitoring well ID. 
```{r}
# add basemap w/leaflet
suppressPackageStartupMessages({
  library(raster)
  library(leaflet)
  library(dplyr)
  library(htmltools)
})
MW_label <- read.csv('MW_label.csv')
# idw
idw1617@crs <- sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
pal <- colorNumeric(c("#9e0142", "#d53e4f", "#f46d43", "#fdae61", "#fee08b", "#e6f598", "#abdda4", 
"#66c2a5", "#3288bd", "#5e4fa2"), values(krige1617), na.color = "transparent")
pal2 <- colorNumeric(c("#9e0142", "#d53e4f", "#f46d43", "#fdae61", "#fee08b", "#e6f598", "#abdda4", 
"#66c2a5", "#3288bd", "#5e4fa2"), values(idw1617), na.color = "transparent")

leaflet() %>% addTiles %>% 
  addProviderTiles(providers$OpenTopoMap) %>% 
  addRasterImage(idw1617, colors = pal2, opacity = 0.85) %>%
  addLegend(pal=pal2, values = values(idw1617), title = "IDW Recharge Estimates 2016-17(m)")%>%   
  addCircleMarkers(data = MW_label, radius = 2, popup = ~as.character(name), label = ~as.character(name), labelOptions =   labelOptions(noHide=T, textOnly = T)) %>%
  addScaleBar(position=c("bottomright"))

# krig
krige1617@crs <- sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

leaflet() %>% addTiles %>% 
  addProviderTiles(providers$OpenTopoMap) %>% 
  addRasterImage(krige1617, colors = pal, opacity = 0.85) %>%
  #addLegend(pal=pal, values = values(krige1617), title = "Kriged Recharge Estimates 2016-17 (m)") %>%
  addMarkers(data = MW_label, popup = ~as.character(name), label = ~as.character(name),  labelOptions = labelOptions(noHide=T, textOnly = T)) %>%
  addScaleBar(position=c("bottomright"))
```

## Results

The recharge estimate found using kriging was **5401 +/- 1351** acre feet or **4.8 +/- 1.2** acre feet per acre. The recharge estimate found using inverse distance weighting was **5820 +/- 1455** acre feet per acre or **5.1 +/- 1.3** acre feet per acre. 

These values represents change in Oneto-Denier groundwater volume from the time at which groundwater level was lowest to the time it was highest. These estimations do not consider seepage due to groundwater presence over time. 
```{r}

```

## Oneto-Denier Field Site
```{r}
library(sp)
library(magrittr)
library(leaflet)
krige1617@crs <- sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

leaflet() %>%  setView(lng = -121.38043, lat = 38.30191, zoom = 14) %>% 
  addTiles() %>% 
  addCircleMarkers(data = MW_label, radius = 2, 
                   color = "black", 
                   popup = ~as.character(name), 
                   label = ~as.character(name),
                   labelOptions = labelOptions(noHide=T)) %>% 
  addProviderTiles(providers$HERE.terrainDayMobile) %>%
  addScaleBar(position=c("topright"))
  
```

## Groundwater Observatory Extent
```{r}
krige1617@crs <- sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")

GO_OD_label <- read.csv('GO_label_ODonly.csv')
GO_label <- read.csv('GO_label.csv')
samer <- read.csv('ohwd_samer.csv')

map <- leaflet() %>%  fitBounds(lng1 = -121.764809, lat1 = 38.227236, lng2 = -121.022671, lat2 = 38.595049) %>% 
  addTiles() %>% 
  addCircleMarkers(data = GO_label, popup = ~as.character(name), radius = 4, color = "black", label = ~as.character(name)) %>% 
  addCircleMarkers(data = GO_OD_label, popup = ~as.character(name), radius = 4, color = "black", label = ~as.character(name)) %>%
  addCircleMarkers(data = samer, popup = ~as.character(name), radius = 4, color = "black", label = ~as.character(name)) %>% 
  addProviderTiles(providers$Hydda.Full) %>%
  addScaleBar(position = c('topright'))
map

```

## Clip IDW to Inundation Extent
```{r}
library(ggplot2)
library(magrittr)
library(dplyr)
library(raster)
# import outline of boundary, as a set of points in lat/long that we generated in ArcMap as a digitized polyline
bound <- read.csv("bound_table.csv", stringsAsFactors = FALSE, header = TRUE)
bound_pts <- bound[,c(4,5)]
colnames(bound_pts) <- c('x', 'y')

# convert raster to SPDF, or at least get some coords
idw1617_pts <- coordinates(idw1617)[!is.na(values(idw1617)),]
colnames(idw1617_pts) <- c('x', 'y')

# clip idw_h by the innundation extent generated form our digitized polyline in ArcMap
library(splancs)
temp <- rasterToPoints(idw1617) %>% as.data.frame()
idw1617_clip <- temp[inout(idw1617_pts, bound_pts), ]
colnames(idw1617_clip) <- c('x','y','z')

# plot idw_h_clip as a heatmap
library(viridis)
library(magrittr)
idw1617_clip %>% 
  ggplot() +
  geom_tile(aes(x,y, fill = z)) +
  coord_fixed(1.3) +
  scale_fill_viridis(name="Recharged Head (m)") +
  theme_void()
# plot trimmed idw on ggmap
library(ggmap)
b <- bbox(low)

 ggplot(idw1617_clip) + 
 geom_tile(aes(x,y, fill = z)) +
  coord_fixed(1) +
  scale_fill_viridis(name="Recharged Head (m)") +
  theme_void() 
 
```

## Add basemap to trimmed flood recharge estimate figure
```{r}
# add basemap w/leaflet
suppressPackageStartupMessages({
  library(raster)
  library(leaflet)
  library(dplyr)
  library(htmltools)
})
MW_label <- read.csv('MW_label.csv')

# idw
pal <- colorNumeric(c("#9e0142", "#d53e4f", "#f46d43", "#fdae61", "#fee08b", "#e6f598", "#abdda4", 
"#66c2a5", "#3288bd", "#5e4fa2"), values(krige1617), na.color = "transparent")

#convert data.frame to spatial polygons data frame 
#coordinates(idw1617_clip) <- ~ x + y
idw17raster <- raster(idw1617_clip)
idw17raster@crs <- sp::CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
pal2 <- colorNumeric(c("#9e0142", "#d53e4f", "#f46d43", "#fdae61", "#fee08b", "#e6f598", "#abdda4", 
"#66c2a5", "#3288bd", "#5e4fa2"), values(idw17raster@z), na.color = "transparent")
# add Spatial Polygons Data Frame to leaflet
leaflet() %>% addTiles %>% 
  addProviderTiles(providers$OpenTopoMap) %>% 
  addRasterImage(idw17raster, colors = rainbow, opacity = 0.85) %>%
  addLegend(pal=pal2, values = values(idw17raster), title = "Event Recharge (m)") %>%
  addCircleMarkers(data = MW_label, popup = ~as.character(name), color = "black", label = ~as.character(name))

```

## Flood Event Recharge 
```{r}
# when event of interest is chosen, replace idw1617_clip with the difference of the high and low gw levels
idwflood_feet <- idw1617_clip*3.28084
ac_per_cell <- 1136/10000
sum_idw_ft <- sum(idw1617_clip$z)
floodrech1617_acft <- sum_idw_ft*ac_per_cell

```

