---
title: "Recharge Function"
author: "Alysa M. Yoder"
date: "June 25, 2018"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE,
                      error = FALSE, 
                      cache = TRUE)
library(here)
```

## Notes
Supplementary material to the recharge volume calculator function.
Actual function is in rech_fxn.R, this 'rech_fxn.Rmd' has the formatting and its where I'll actually do the calculations of recharge. 

> Rules: 
* import water levels at the beginning and end of the event
* input files' columns must be in this order: lat, long, level
* the 'level' column must be in meters of groundwater elevation relative to mean sea level

***

## Get Groundwater Level Data
```{r}
adata <- read.csv(here('data', 'allsets.csv'), stringsAsFactors = FALSE)
adata <- adata[-c(1,3,15,17:31)] #removing index numbers, MW-13, Oneto-Ag (confined), and Nathan's text 
```

## Get Lat Long Coordinates for Each Well 
```{r}
# format dataframes w/lat long 
label <- read.csv(here('data', "MW_label_allsets.csv"), header = F) #get lat long data, already in order of allsets.csv wells
label[3] <- NULL #removes well ID text column, leaving only lat long coords
```

## Get Data from Desired Dates
```{r}
# grab max and mins from each water year. 
max2014 <- as.data.frame(t(subset(adata, Date == "2014-05-10 12:00:00")))
min2014 <- as.data.frame(t(subset(adata, Date == "2014-02-09 12:00:00")))

```

## 2015 formatting
```{r}
max2015 <- as.data.frame(t(subset(adata,Date =="2015-04-12 12:00:00")))

rownames(max2015) <- NULL

colnames(max2015) <- NULL
max2015 <- max2015[-1,]
max2015
hi2015 <- data.frame(c(label,max2015))
colnames(hi2015) <- NULL
rownames(hi2015) <- NULL
colnames(hi2015) <- c("lat", "long", "level")
hi2015 <- read.csv("hi2015.csv")

min2015 <- as.data.frame(t(subset(adata,Date =="2014-12-04 12:00:00")))
rownames(min2015) <- NULL
colnames(min2015) <- NULL
min2015 <- min2015[-1,]
lo2015 <- data.frame(c(label,min2015))
colnames(lo2015) <- NULL
rownames(lo2015) <- NULL
colnames(lo2015) <- c("lat", "long", "level")
lo2015 <- read.csv("lo2015.csv")

```

```{r}
## 2016 formatting
max2016 <- as.data.frame(t(subset(adata,Date =="2016-03-18 12:00:00")))
rownames(max2016) <- NULL
colnames(max2016) <- NULL
max2016 <- max2016[-1,]
hi2016 <- data.frame(c(label,max2016))
colnames(hi2016) <- NULL
rownames(hi2016) <- NULL
colnames(hi2016) <- c("lat", "long", "level")

min2016 <- as.data.frame(t(subset(adata,Date=="2016-12-10 12:00:00")))
rownames(min2016) <- NULL
colnames(min2016) <- NULL
min2016 <- min2016[-1,]
lo2016 <- data.frame(c(label,min2016))
colnames(lo2016) <- NULL
rownames(lo2016) <- NULL
colnames(lo2016) <- c("lat", "long", "level")

```

## 2014 Formatting
```{r}
# below is working code for formatting a recharge estimate input file
min2014 <- as.data.frame(t(subset(adata, Date == "2014-02-09 12:00:00")))
rownames(min2014) <- NULL
colnames(min2014) <- NULL
min2014 <- min2014[-1,]
lo2014 <- data.frame(c(label,min2014))
colnames(lo2014) <- NULL
rownames(lo2014) <- NULL
colnames(lo2014) <- c("lat", "long", "level")

# put data filenames into begin and end variables, run above lines, use function 'rechvol' with begin=begin and end=end to get m^3 recharge volumes
begin <- read.csv("R_input_low_1617.csv")
end <- read.csv("R_input_high_1617.csv")

# make sure column names are compatible with the function
colnames(hi2014) <- c("lat", "long", "level")

```


## Comparison of Similar Event Pre&Post Levee Removal
```{r}
#recharge event max and min GWLs pre-removal, during the 2014 WY
evlo14 <- as.data.frame(t(subset(adata, Date == "2014-02-10 02:15:00")))
evhi14 <- as.data.frame(t(subset(adata, Date == "2014-02-12 05:30:00")))

#clean up data to get just water levels
#low
rownames(evlo14) <- NULL
colnames(evlo14) <- NULL
evlo14 <- evlo14[-1,]
evlo14 <- data.frame(c(label,evlo14))
colnames(evlo14) <- NULL
rownames(evlo14) <- NULL
colnames(evlo14) <- c("lat", "long", "level")
#high
rownames(evhi14) <- NULL
colnames(evhi14) <- NULL
evhi14 <- evhi14[-1,]
evhi14 <- data.frame(c(label,evhi14))
colnames(evhi14) <- NULL
rownames(evhi14) <- NULL
colnames(evhi14) <- c("lat", "long", "level")

#use function for 2014 event 
rechvol(begin = evlo14, end = evhi14, plot_title = "2014WY Event")

#repeat all for 2015 wY
```

